Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-05 Submission.Rmd
See line 351 and triple check this code!!

sortresource <- resource[order(resource$sd),]

>>>>

resource <- resource[,-145]   ## attention check
#resource <- resource[ which(resource$sd > 0), ] 
########################################################
########################################################
##Need to triple check all of this. 
########################################################
########################################################
##checking the ns
library(psych)
resource_ns <- describe(data[c(118:144, 146:202)])
#resource_ns
#table(data$item161) # check one item to confirm ns - it is functioning correctly.

resource <- cbind(resource, resource_ns$n)
resource
sortresource <- resource[order(resource$sd),]
